---
title: "AirBnB"
author: "Shaun Jose"
date: "11/29/2021"
output: html_document
---


library(ggplot2)
library(ggthemes)
library(dplyr)
library(scales)
library(knitr)
library(lubridate)
library(tidyr)
library(ggridges)
library(leaflet)


```{r}
airbnb <- read.csv("AB_NYC_2019.csv")
airbnb$last_review <- ymd(airbnb$last_review)
str(airbnb)
airbnb <- na.omit(airbnb)
dim(airbnb)
summary(airbnb)
str(airbnb)
```



## Prices of Different Types of Room

```{r}
ggplot(airbnb, aes(room_type, price)) +
   geom_boxplot(aes(fill = room_type)) +
   scale_y_log10() +
   labs(title = "Price by Room Type", x= "Room Type", y= "Price", fill = "Room Type",
        subtitle = "Red line indicates the average price") +
   theme(plot.title = element_text(hjust = 0.5)) +
   geom_hline(yintercept = mean(airbnb$price), color = "red", linetype = 5)
```
Observations:
1. Home/Apartment type rooms have the highest average price compared to private rooms and shared rooms. 
2. Private rooms and shared rooms are the cheapest options available to customers as it falls below the average price line.


## Relationship between Availability and Price

```{r}
ggplot(airbnb, aes(availability_365, price)) +
  geom_point(alpha = 0.5, color = "green") + 
  geom_segment(aes(x=availability_365, xend=availability_365, y=0, yend=price)) +
  labs(title = " Relationship between Availability and Price", x ="Yearly Availability", y= "Price")+
  theme(plot.title = element_text(hjust = 0.5))
```
Observations:
1. Higher prices generally have lower availability.
2. Lower prices are correlated with high availability throughout the year. 
3. It's surprising to see that for prices above 5000, the yearly availability can be over 50 days. 


## Availaibilty in Boroughs 

```{r}
ggplot(airbnb,aes(room_type,availability_365))+
   geom_violin(aes(fill = neighbourhood_group,width = .9)) +
   labs (title = "Availability in Boroughs", x = "Room Type", y = "Availability", fill ="Boroughs")+
   theme(plot.title = element_text(hjust = 0.5))
```
Observations:
1. Brooklyn and Manhattan's private room availability is similar to each other
2. Brooklyn and Manhattan's entire home/apt availability is similar to each other.
3. Staten island's share room availability is lower than all the other boroughs. 

## Price Distribution of Different Boroughs for Entire Home/Apt Type

```{r}
head(airbnb[airbnb$room_type == "Entire home/apt",]) 
era <- airbnb[airbnb$room_type == "Entire home/apt",]
dim(era)
P <- function(x){
   if (x<300) {x<-"Below 300"} else if (x>=300 & x<=500) {x <- "300 to 500"} else if (x>500 & x<1000) {x <-"between 500-1000"} else {x <- "above 1000"}}

era$priceC <- as.factor(sapply(era$price, P))
head(era)
```
```{r}
ggplot(era,aes(neighbourhood_group,price)) +
   geom_jitter(aes(col= era$priceC)) +
   geom_boxplot(alpha=0.5) +
   scale_y_log10()+
   labs(title = "Rental Rates in different Neighbourhoods", x= "Neighbourhood", y= "Price", col = "Rental Rate") +
   theme(plot.title = element_text(hjust = 0.5))
```
Observation:
1. Prices in Manhattan are distributed well compared to the other boroughs where majority of the prices of the rentals are below 300 in Manhattan.
2. Brooklyn closely mirrors Manhattan's distributions but has fewer rentals for prices between 300 and 500 and higher number of rentals for prices below 300 compared to Manhattan
3. There are very rentals with prices ranges of 300-500, 500-1000 and greater than 1000 in Staten Island
4. Bronx has no rentals for prices between 500-100. 


## Average Value of Minimum Night and Review of Each Boruough for Entire Home/Apt Type

```{r}
head(aggregate.data.frame(list(Review = era$number_of_reviews, Nights = era$minimum_nights), by = list(Neighbourhood = era$neighbourhood_group), mean))

eraRN <- aggregate.data.frame(list(Review = era$number_of_reviews, Nights = era$minimum_nights), by = list(Neighbourhood = era$neighbourhood_group), mean)
dim(eraRN)

eraRN <- gather(eraRN, key = "variable", value = "average", -Neighbourhood)
eraRN
```


```{r}
ggplot(eraRN,aes(Neighbourhood, average))+
   geom_col(aes(fill = variable), position = "dodge") +
   coord_flip()+
   labs(title = "Average Night and Review for each Neighbourhood", x= "Group of Neighb", y = "Value", fill = "Variable")+
   geom_text(aes(label=comma(average)), hjust = -0.2, size = 3)+
   theme(plot.title = element_text(hjust = 0.5))
```
Observations:

1. Manhattan leads with the highest average nights spent by a guest renting an entire home/apt
2. Staten Island has the highest average for number of reviews compared to other boroughs while having the lowest amount of nights spent by a customer.

## Relationship between number of reviews and prices in Brooklyn and Manhattan

```{r}
A <- airbnb[order(airbnb$price, decreasing =T),]
airbnbM_B <- A [A$neighbourhood_group== "Manhattan" | A$neighbourhood_group== "Brooklyn", ]
head(airbnbM_B)
```


```{r}
ggplot(airbnbM_B, aes(price, number_of_reviews)) +
   geom_jitter(aes(col = number_of_reviews))+
   scale_x_log10()+
   facet_wrap(~neighbourhood_group, scales = "free")+
   labs(title = "Correlation between Price and Review", x="Price", y= "Number of Reviews" )+
   theme(plot.title = element_text(hjust = 0.5))
```
Observations:
1. There isn't a noticeable relationship between reviews and price for the boroughs of Brooklyn and Manhattan.


## Duration of stay in Manhattan and Brooklyn
```{r}
airbnbM_B$year <- year(airbnbM_B$last_review)
airbnbM_B$year <- as.factor(airbnbM_B$year)
head(airbnbM_B$year)
```

```{r}
ggplot(airbnbM_B,aes(minimum_nights, year)) +
   geom_density_ridges(fill="yellow")+
   scale_x_continuous(limits = c(0,100),breaks = seq(0,100,10))
```
Observations: 
1. A common trend among the years is that majority of the peaks are around 5-8 nights spent by a customer.
2. Between 2012 - 2019, there have been slight peaks at 30 nights spent by a customer.

## Host with the highest amount of reviews

```{r}
host <- airbnb[match(unique(airbnb$host_id), airbnb$host_id), ]
host <- host[order(host$number_of_reviews, decreasing = T), ]
host <- host[1:30, ]
host
```



```{r}
ggplot(host,aes(reorder(host$host_name,host$number_of_reviews), host$number_of_reviews))+
   geom_col(fill ="magenta")+
   facet_grid(rows = vars(neighbourhood_group), scales = "free_y")+
   geom_point(aes(col=price))+
   geom_text(aes(label= comma(host$number_of_reviews)), hjust=-0.4, size = 3)+
   labs( x="Host Name", y= "Reviews")+
   coord_flip()
```
Observations: 
1. Dona from Queens has the highest number of reviews with more than 600 reviews from customers and the price of her listing is below $100
2. Hosts from Queens have better average number of reviews compared to other Boroughs
3. Staten Island and Bronx are not included in the top 30 number of reviews.

## Which Borough has the most number of listings?
```{r}

city <- data.frame(distinct(airbnb,name,latitude,longitude))


city[city == "NULL"] <- NA


city <- city[complete.cases(city[,1:3]),]

testMap <- leaflet() %>%
  addTiles() %>% 
  addMarkers(lat = airbnb$latitude, lng = airbnb$longitude, popup = airbnb$name, clusterOptions = markerClusterOptions())

testMap

```
Observations:
1. Manhattan has the highest number of listings with over 25,000 listings.
2. Staten Island has the lowest number of listings.


```{r}
city <- data.frame(distinct(airbnb,name,price,latitude,longitude))


city[city == "NULL"] <- NA


city <- city[complete.cases(city[,1:3]),]
pricetop <- arrange(city, (airbnb$price))[1:10,]
str(pricetop)

testMap <- leaflet() %>%
  addTiles() %>% 
  addMarkers(lat = airbnb$latitude, lng = airbnb$longitude, popup = airbnb$name, clusterOptions = markerClusterOptions())

testMap


leaflet(pricetop) %>% 
  addTiles() %>%
  addMarkers(lng = ~longitude, lat = ~latitude, popup = airbnb$name)

```




```{r}
city <- data.frame(distinct(airbnb,name,price,latitude,longitude))


city[city == "NULL"] <- NA


city <- city[complete.cases(city[,1:3]),]
pricetop <- arrange(city, (airbnb$price))[1:10,]
str(pricetop)

leaflet(pricetop) %>% 
  addTiles() %>%
  addMarkers(lng = airbnb$longitude, lat = airbnb$latitude, popup = airbnb$name)
```

